Mo' Betta Gaia Distance Measurements, \\ Using Gaia + APASS photometry

### 2017-02-08 paperDistance/paper.tex
acks

>>>>

This project was developed in part at the 2016 \acronym{NYC} Gaia Sprint, hosted
by the Center for Computational Astrophysics at the Simons Foundation
in New York City.

This work has made use of data from the European Space Agency (\acronym{ESA})
mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia
Data Processing and Analysis Consortium (\acronym{DPAC},
http://www.cosmos.esa.int/web/gaia/dpac/consortium). Funding for the
\acronym{DPAC} has been provided by national institutions, in particular the
institutions participating in the Gaia Multilateral Agreement.

[IS THERE A \tmass\ ACKNOWLEDGEMENT?]

This project was partially supported by [DWH GIVE GRANT NUMBERS]. It
made use of the \acronym{NASA} Astrophysics Data System.
